---
title: "Esmating Covid-19 Rt"
author: "Rui Hu(rh2835)"
date: "4/17/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

  This is a self-learning project from the following tutorial on datacamp: https://www.datacamp.com/community/tutorials/replicating-in-r-covid19

# Bettencourt & Ribeiro   
## Modeling arrivals    
  Using Poisson Distribution to model the 'arrival' process of infections. Let $\lambda$ be the average rate of infections per day, then the probability of $k$ new cases on a day is given by $$P \left( k|\lambda \right) = \frac{\lambda^k e^{-\lambda}}{k!}$$

## Code setup
```{r}
library(tidyverse)

#Plot options, custom theme
options(repr.plot.width = 12, repr.plot.height = 6)
theme_custom <- function(base_size, ...){
  ggplot2::theme_gray(base_size = base_size, ...) +
  ggplot2::theme(
    plot.title = element_text(face = 'bold'),
    plot.subtitle = element_text(color = '#333333'),
    panel.background = element_rect(fill = "#EBF4F7"),
    strip.background = element_rect(fill = "#33AACC"),
    legend.position = "bottom"
  )
}
ggplot2::theme_set(theme_custom(base_size = 20))
ggplot2::update_geom_defaults("line", list(size = 1.5))

# Utility functions
display_df <- function(x){
  d <- as.character(
    knitr::kable(x, format = 'html', table.attr = "class='dataframe'")
  )
  IRdisplay::display_html(d)
}

display_head <- function(x, n = 6){
   display_df(head(x, n))
}

display_random <- function(x, n = 6){
   display_df(dplyr::sample_n(x, n))
}
```


## Poisson distribution
```{r}
# Number of new cases observed in a day
k = 0:69

# Arrival rate of new infections per day
lambda = c(10, 20, 30, 40)

library(purrr)
# reference for purrr: https://bookdown.org/content/922/tidyverse.html
possion_densities = crossing(lambda = lambda, k = k) %>%
  mutate(p = dpois(k, lambda))

head(possion_densities)
```


```{r}
# This chunk is to review some common used functions in tidyverse
library(tidyverse)
rnorm(mean = 0, sd = 1, n = 5)

mu = list(5, 15, -5)
mu %>%
  map(rnorm, n = 5) %>%
  str()

params <- tribble(
  ~n, ~mean, ~sd,
  10, 0, 1,
  20, 5, 1,
  30, 10, 2
)
params %>%
  pmap(rnorm) %>%
  str()

f <- c("runif", "rnorm", "rpois")
param <- list(
  list(min=-1, max=1),
  list(sd = 5),
  list(lambda = 10)
)
invoke_map(f, param, n = 10) %>% str()

sim <- tribble(
  ~f, ~params,
  "runif", list(min = -1, max = 1, n = 10),
  "rnorm", list(sd = 5, n = 15),
  "rpois", list(lambda = 10, n = 30)
)
sim %>%
  mutate(sim = invoke_map(f, params))


n_tosses = 10
one_exp <- rbinom(p = 0.5, size = 1, n_tosses)
mean(one_exp)

sim <- tribble(
  ~f, ~params,
  "rbinom", list(size = 1, prob = 0.5)
)
sim %>%
  mutate(sim = invoke_map(f, params, n = 10)) %>%
  unnest(sim) %>%
  summarise(mean_sim = mean(sim))

sim <- tribble(
  ~f, ~params,
  "rbinom", list(size = 1, prob = 0.5)
)
rep_sim <- sim %>%
  crossing(rep = 1:1e2) %>%
  mutate(sim = invoke_map(f, params, n = 10)) %>%
  unnest(sim) %>%
  group_by(rep) %>%
  summarise(mean_sim = mean(sim))
head(rep_sim)

```


Visualize these probabilities using ggplot2.
```{r}




```



```{r, echo=FALSE}
plot(pressure)
```







## References:
http://systrom.com/blog/the-metric-we-need-to-manage-covid-19/  
https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0002185
